\section{Autism}

Autism is a spectrum disorder, which appears in the first three years of a child's life. It affects the development of the brain that has to do with social and communication skills. Autism affect how information is processed in the brain by altering how the brain's nerve cells and synapses connect. How this is occurs is not very well understood.\citep{autism} There are different diagnosis of autism:

\begin{itemize}
\item \textbf{ADHD} Attention Deficit/Hyperactivity Disorder
\item \textbf{Tourette} Verbal and motor tics
\item \textbf{Chromosomal defects}
\end{itemize}

Autism is a physical condition and it is linked to an abnormal chemistry in the brain, however the exact causes of these abnormalities are still unknown.\citep{autism} 

\subsection*{Symptoms} 

Children with autism usually have a hard time with "pretend to play", they have a hard time imitating the actions of others when playing and prefer to play alone. They also have difficulties with social interaction and communication - verbally and non-verbally. 

In general people with autism may:

\begin{itemize}
\item Be very sensitive to sight, hearing, touch, or taste.
\item Have a very hard time adjusting to new routines and when routines are changed.
\item Show unusual attachments to objects
\end{itemize} 

The difficulties with social interaction means that people with autism may have a hard time starting and maintaining a social conversation, they communicate with gestures instead of words, develops language slowly and some develops none at all. 

The lack of social interaction means they might have a hard time making friends, they may be withdrawn and avoid eye contact.\citep{autism}

\subsection*{Signs and tests}

Some of the signs that parents might need to further test their child for autism are if the child fails to meet any of the following language milestones:

\begin{description}
\item Babbling by 12 months
\item Gesturing (such as pointing or waving goodbye) by 12 months
\item Saying single words by 16 months
\item Losing any language or social skills at any age
\end{description}

Children failing to meet any of those language milestones might receive a hearing evaluation, a blood test and a screening test for autism. Since autism includes a broad spectrum of symptoms, a single brief evaluation cannot predict what abilities the child might have, therefore a range of different skills are evaluated, such as:

\begin{itemize}
\item Communication
\item Language
\item Motor skills
\item Speech
\item Success at school
\item Thinking abilities
\end{itemize}

Some parents might be scared of getting their child diagnosed because they are scared of labelling it, however without a diagnosis the child might not get the necessary help.\citep{autism} 

\subsection*{Treatment}

Autism cannot be cured, however an early diagnosis and treatment can greatly improve the child's life. The different programs usually build on the child's interests and is highly structured as they need their routines.\citep{autism}